Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-16 Manuscript/manuscript.tex
MS update: improved reasoning around PN-vector and S_CD connection, explained simulation system composition, creation of ECC-surfactant, added many references to ion models, corrected some names, checked scattering form factor equiation sanity.

Lipid bilayer structure without ions was validated against NMR experiments
by order parameters for C-H bonds and x-ray scattering experiments by using
form factors. The former validates the structures sampled by individual
lipid molecules in simulations with segmental resolution, while the latter
validates the dimensions of the lipid bilayer (thickness and area per
molecule)~\cite{ollila16}.

Order parameters were calculated from simulations for all C-H bonds
by using Eq. \ref{OP} and form factors as
\begin{equation}
  F(q) = \int _{-D/2} ^{D/2} \left ( \sum _\alpha f_\alpha (q_z) n_\alpha (z) - \rho _s \right ) \exp (izq_z) \mathrm{d}z,
\end{equation}
where $f_\alpha(q_z)$ is the density of atomic scattering length, 
$\rho_s$ is the density of solvent scattering lenght,
$n_\alpha (z)$ is the number density of atom $\alpha$ and
$z$ is the distance from the membrane centre along its normal 
spanning the membrane with thickness $D$.

@@

\subsubsection{Simulations with aqueous ions}
The simulated systems consisted of 1-Palmitoyl-2-oleoylphosphatidylcholine
(POPC) bilayer and an aqueous salt solutions of varying concentrations.
Water molecules were described by OPC3 model \cite{Izadi16}
\todo{Explain why were OPC3 chosen}.
In order to test transferability of the newly developed ECC-lipids model, 
we also performed several additional simulations with water models 
OPC \cite{Izadi14}, SPC/E \cite{Berendsen1987} and TIP4p/2005 \cite{Abascal2005}
presented in Supporting Information (SI). 
We used ECC-ions model for ions \cite{jungwirth17-new-paper-to-be-published, kohagen16, Pluharova2014}.  % cite order: [Ca_2s, Na_s, Cl_2s]
Simulations with Lipid14 use ion model by Dang \cite{smith94,chang1999,dang2006}. 
Classical molecular dynamics simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4).  
The simulation settings used in this work are 
summarized in Table \ref{tbl:mdpar}, 
and they are based on previously used settings in \cite{catte16} available at \cite{lipid14POPC0mMNaClfiles}. 
Simulation trajectories and parameters are available at \cite{??} \todo{To be uploaded to Zenodo}. \\
\todo{System sizes has to reported somewhere}

@@

\subsubsection{Simulations with cationic surfactants}
Automated topology builder \cite{malde11} was first used to create the structure of
dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$, molecule.
AmberTools program \cite{amber} was then used to generate the Amber-type force field
parameters. The parameters were converted to the Gromacs format by using
acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond to their equivalent segments in Lipid14 \cite{dickson14}.
The surfactants were randomly placed among the lipids to form bilayer structures with
mole fractions 10\%, 20\%, 30\%, 42\% and 50\% of surfactant in the POPC bilayer.
All systems contained 50 POPC molecules per leaflet, 6340 TIP3P water molecules and
6, 14, 21, 35 or 50 surfactants per leaflet.
These systems were first simulated 200~ns by using Lipid14 model.
First 20~ns was omitted from the analysis.

The same systems where also simulated with ECC-corrected lipi model...
\todo{Describe the changes in surfactant model used with ECC-corrected lipids.}

@@

\subsection{Response of POPC headgroup on bound charge}

@@

The headgroup response to bound charge depends on both, the
binding affinity and the response of the headgroup on bound charge.
Thus, the headgroup response to bound charge has to be correctly
described in the model if the concept is used for quantitative studies of
binding affinity. Hence, we first quantify the response of head group order
parameters to the bound charge by using experimental data measured from
mixtures of cationinc surfactants and PC lipids~\cite{scherer89}.
The amount of the bound charge is known excatly in these systems,
because essentially all surfactants with unit charge locate in lipid bilayers.
%Thus, the headgroup order parameter response to bound charge can be first
%quantified aginst experimental data before proceeding to binding affinity studies.
%Headgroup order parameter response to the amount of bound charge can
%be quantified by using ionic surfactants with a known valency~\cite{scherer89}.
%All surfactants locate in lipid bilayers due to their amphiphilic nature,
%thus the exact amount of bound charge in the membrane is known in these systems.
%The headgroup order parameter changes as a function of bound charges can be then
%explicitly determined from such systems.

Changes of headgroup order parameter as a function of added cationic surfactant
dihexadecyldimethylammonium bromide (C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) from
experiments~\cite{scherer89} and simulations are shown in
Fig. \ref{OrderParameterCHANGESsurf}).
As expected from Eq. \ref{OPchangeEQ}, the head group order parameter response to the bound cation concentration
is approximately linear at least up to $\sim$0.3 mole fraction in experiments and
in both simulation models, original Lipid14 and ECClipids \todo{Yet to be shown.}. 
\todo{We might want to calculate the slopes from simulations.}

The slope is, however, too steep in Lipid14 model indicating that the
headgroup order parameters are too sensitive for bound charge in this model.
This has to be taken into account when interpreting the
headgroup order parameter response to CaCl$_2$ concentration in Lipid14 model.
%observed in  Ref. \citenum{catte16}, see also Fig. \ref{OrderParameterCHANGESnewMODELS}.
The ECC-lipids model gives a slope in very good agreement with experiments
for the $\alpha$ segment, while the slope is slightly
underestimated for the $\beta$ segment.
%The present comparison of head group order parameter changes 
%suggests that the observed overestimated response of all models to 
%increasing CaCl$_2$ concentration in \cite{catte16} 
%can be explained at least in part by a high sensitivity of the head group order parameter response
%to the bound charge.

Also the angle of the headgroup P-N vector with respect to membrane normal
is shown in Fig.~\ref{OrderParameterCHANGESsurf} as a function of bound cations.
As expected~\cite{seelig87}, the headgroup orients more parallel with membrane
normal with increasing amount of bound cations. The effect is stronger
in Lipid14 parameters than in ECClipid parameters, which is in line
with the reduced dipole moment and the lower sensitivity to bound charges
in the ECClipid model.
\todo{It might be a good idea to establish a relation between order parameter change
and P-N vector angle by using ECClipids model.}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of NaCl, CaCl$_2$ concentration
    from simulations with different force fields and experiments (DPPC \cite{akutsu81} and POPC \cite{altenbach84}).
    Simulations with Lipid14 parameters and Aqvist ions are directly from Ref. \cite{catte16}, except that
    the concentration are determined with Eq. \ref{eq:conc}.
  }
  \todo{Simulation results with original Slipids and Dang ions to be added when we have the results.}
\end{figure*}

%After achieving accurate head group order parameter response with a cationic surfactant, 
%we advanced to quantifying the response to solutions with varying concentrations of salts, namely \ce{NaCl} and \ce{CaCl_2}.
The headgroup order parameter response to aqueous ionic concentration
can be used to measure ion binding affinity in experiments and simulations,
as discussed in section \ref{section:electrometer} and in previous literature~\cite{seelig87,catte16}.
The headgroup order parameter response of PC lipids to NaCl and CaCl$_2$ concentrations
from experiments (DPPC \cite{akutsu81} and POPC \cite{altenbach84}) and different simulation
models are shown in Fig. \ref{OrderParameterCHANGESnewMODELS}.
The simulation results of Lipid14 with Aqvist ions \cite{??} (from Ref. \citenum{catte16})
are shown together with the results from Lipid14 simulation
with Dang ions \cite{??} and from ECClipid simulations with ECC-ions.

As already discussed in the recent work by NMRlipids project~\cite{catte16},
the headgroup order parameters are almost unaffected by addition of NaCl
in Lipid14 simulations with Aqvist ion model due a very weak binding of Na$^+$
in PC bilayer. This is in agremeent with experimental data, in contrast
to almost all the other lipid models, which significantly overestimate
Na$^+$ binding in PC bilayers~\cite{catte16}. Despite of good performance
with NaCl, the response of headgroup order parameters to CaCl$_2$ concentration are
significantly overestimated in Lipid14 simulations with Aqvist ion model,
see Fig.~\ref{OrderParameterCHANGESnewMODELS} and \citenum{catte16}.

Wide range of data presented in previous work \cite{catte16} suggested
that CaCl$_2$ binding behaviour cannot be corrected by only improving
ion models. This was not, however, tested for Lipid14 model, so we
ran also Lipid14 simulations with Dang \cite{smith94,chang1999,dang2006} and ECC corrected \cite{??}
ions having more realistic bulk behaviour as Aqvist model \cite{??}.
In line with previous work, the headgroup order parameters response
to CaCl$_2$ concentartion was overestimated also with these ion models,
as seen in Figs. \ref{OrderParameterCHANGESnewMODELS} and \ref{??} (in SI), respectively
\todo{Add OP-response of Lipid14+Dang in Fig. \ref{OrderParameterCHANGESnewMODELS}
  and OP-response of Lipid14+ECC-ions plot in SI}.

Applying ECC correction also for lipids, introduced in section \ref{section:ecc},
brings the order parameter response to CaCl$_2$ concentration to a
good agreement with experiments, as shown in Fig. \ref{OrderParameterCHANGESnewMODELS}.
This is a significant improvement over previously introduced models,
which all overestimate the head group order parameter response to CaCl$_2$
concentration \cite{catte16}. The good agreement with experiments indicates
that the ECC corrected lipid model has a sufficient accuracy for realistic
studies of ion binding details on lipid bilayers.

Ion density profiles along membrane normal coordinate
from different simulations are shown in Fig.~\ref{fig:cacl-dens}.
\todo{This paragraph is to be finalized when we have the surface excess analysis
  done by using Eq.~\ref{surfexcess}.}
This is directly related to the amount of surface excess charge 
as shown along with ion density profiles in  Fig.~\ref{fig:cacl-dens}.
The density profiles from simulations with original Lipid14 \cite{dickson14}
and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
or the standard Amber ion model by \AA{qvist}~\cite{aqvist90}
along with Lipid14 does not significantly change it 
(Headgroup order parameter responses for these models in SI).
The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
It is then likely that the models that overestimate head group order parameter response~\cite{catte16}
also overestimate the amount of bound cations.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities2.eps}
  \caption{\label{fig:cacl-dens}
    Number density of \ce{Ca^{2+}} and \ce{Cl^-} as a function of membrane normal axis
    for different force fields. Data for Lipid14 with Aqvist ions are taken directly from Ref. \citenum{catte16}
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    Densities of~\ce{Cl^-}) and water are divided with 2 and 200, respectively, to visalize them
    with the same scale as \ce{Ca^{2+}}. The molar concentration in water is 350~mM in all systems
    presented here. 
    }
  \todo{PAVEL: draw phosphate position with its variance, add water density (scaled) and include the number of$\Gamma$-surface access.} \\
  \todo{JOE: Change the figure so that it contains a membrane background} \\
  \todo{Resuls with Lipid14+Dang to be added once done.}
\end{figure}

@@

This work will serve as a foundation stone of a 
new open-collaboration project NMRlipids~VI in nmrlipids.blogspot.fi.

>>>>

Lipid bilayer structure without ions was validated against NMR experiments
by order parameters for C-H bonds and \mbox{x-ray} scattering experiments by using
form factors. The former validates the structures sampled by individual
lipid molecules in simulations with segmental resolution, while the latter
validates the dimensions of the lipid bilayer (thickness and area per
molecule)~\cite{ollila16}.

Order parameters were calculated from simulations for all C-H bonds
by using Eq. \ref{OP} and form factors as
\begin{equation}
  F(q) = \int _{-D/2} ^{D/2} \left ( \sum _\alpha f_\alpha (q_z) n_\alpha (z) - \rho _s \right ) \exp (izq_z) \mathrm{d}z,
\end{equation}
where $f_\alpha(q_z)$ is the density of atomic scattering length, 
$\rho_s$ is the density of solvent scattering length,
$n_\alpha (z)$ is the number density of atom $\alpha$ and
$z$ is the distance from the membrane centre along its normal 
spanning the membrane with thickness $D$.

@@

\subsubsection{Simulations with aqueous ions}
The simulated systems consisted of 1-Palmitoyl-2-oleoylphosphatidylcholine
(POPC) bilayer and an aqueous salt solutions of varying concentrations.
In particular, the periodic orthorhombic simulation box conatined 
128 POPC molecules and approximately 50~water molecules per each lipid.
Water molecules were described by OPC3 model~\cite{Izadi16} 
as it is currently the most accurate three site rigid water model. 
In order to test transferability of the newly developed ECC-lipids model, 
we also performed several additional simulations with water models 
OPC \cite{Izadi14}, SPC/E \cite{Berendsen1987}, TIP3p-FB and TIP4p-FB~\cite{Wang2014}, and TIP4p/2005 \cite{Abascal2005}
presented in Supporting Information (SI). 
We used ECC-ions model for ions \cite{jungwirth17-new-paper-to-be-published, kohagen16, Pluharova2014}.  % cite order: [Ca_2s, Na_s, Cl_2s]
Simulations with Lipid14 use ion models by Dang~\cite{smith94,chang1999,dang2006}, and by \AA{}qvist~\cite{aqvist90}. 
Classical molecular dynamics simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4).  
The simulation settings used in this work are 
summarized in Table \ref{tbl:mdpar}, 
and they are based on previously used settings in \cite{catte16} available at \cite{lipid14POPC0mMNaClfiles}. 
Simulation trajectories and parameters are available at \cite{??} \todo{To be uploaded to Zenodo}.

@@

\subsubsection{Simulations with cationic surfactants}
Automated topology builder \cite{malde11} was first used to create the structure of
dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$, molecule.
AmberTools program \cite{amber} was then used to generate the Amber-type force field
parameters. The parameters were converted to the Gromacs format by using
acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond to their equivalent segments in Lipid14 \cite{dickson14}.
The surfactants were randomly placed among the lipids to form bilayer structures with
mole fractions 10\%, 20\%, 30\%, 42\% and 50\% of surfactant in the POPC bilayer.
All systems contained 50 POPC molecules per leaflet, 6340 TIP3P water molecules and
6, 14, 21, 35 or 50 surfactants per leaflet.
These systems were first simulated for 200~ns using Lipid14 model.
First 20~ns was omitted from the analysis. 
Simulations with ECC-lipids used the same simulation setup.
We also applied electronic continuum correction to the cationic surfactant 
by scaling all its charges with the same factor as for ECC-lipids, $f_q=0.8$, 
and by using the atom types with reduced $\sigma$ parameters from ECC-lipids.

@@

\subsection{Response of POPC headgroup to bound charge}

@@

REWRITE:
The headgroup response to bound charge depends on both, the
binding affinity and the response of the headgroup on bound charge.
Thus, the headgroup response to bound charge has to be correctly
described in the model if the concept is used for quantitative studies of
binding affinity. Hence, we first quantify the response of head group order
parameters to the bound charge by using experimental data measured from
mixtures of cationinc surfactants and PC lipids~\cite{scherer89}.

The amount of the bound charge is known excatly in these systems,
because essentially all surfactants with a unit charge locate in the lipid bilayers.
%Thus, the headgroup order parameter response to bound charge can be first
%quantified aginst experimental data before proceeding to binding affinity studies.
%Headgroup order parameter response to the amount of bound charge can
%be quantified by using ionic surfactants with a known valency~\cite{scherer89}.
%All surfactants locate in lipid bilayers due to their amphiphilic nature,
%thus the exact amount of bound charge in the membrane is known in these systems.
%The headgroup order parameter changes as a function of bound charges can be then
%explicitly determined from such systems.

Changes of headgroup order parameters as a function of added cationic surfactant
dihexadecyldimethylammonium bromide (C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) from
experiments~\cite{scherer89} and simulations are shown in
Fig. \ref{OrderParameterCHANGESsurf}.
As expected from Eq. \ref{OPchangeEQ}, the head group order parameter response to the bound cation concentration
is approximately linear at least up to $30\%$ mole fraction in experiments and
in both simulation models, original Lipid14 and ECC-lipids.  
\todo{We might want to calculate the slopes from simulations.}

The slope of the head group order parameters response is, however, 
too steep in Lipid14 model indicating that 
its head group response is too sensitive to a bound charge. 
This has to be taken into account when interpreting the
head group order parameter response to CaCl$_2$ concentration in Lipid14 model.
%observed in  Ref. \citenum{catte16}, see also Fig. \ref{OrderParameterCHANGESnewMODELS}.
The ECC-lipids model gives a slope in very good agreement with experiments
for the $\alpha$ segment, while the slope is slightly
underestimated for the $\beta$ segment.
%The present comparison of head group order parameter changes 
%suggests that the observed overestimated response of all models to 
%increasing CaCl$_2$ concentration in \cite{catte16} 
%can be explained at least in part by a high sensitivity of the head group order parameter response
%to the bound charge.

Also the angle of the headgroup P-N vector with respect to membrane normal
is shown in Fig.~\ref{OrderParameterCHANGESsurf} as a function of bound cations.
As expected~\cite{seelig87}, the headgroup orients more parallel with the membrane
normal with an increasing amount of bound cations. The effect is stronger
in Lipid14 model than in ECC-lipids model, which is in line
with the reduced charge--dipole interactions in the ECC framework  
leading to the lower head group sensitivity to bound charges in ECC-lipids model.

\todo{It might be a good idea to establish a relation between order parameter change
and P-N vector angle by using ECC-lipids model.}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of NaCl, CaCl$_2$ concentration
    from simulations with different force fields and experiments (DPPC \cite{akutsu81} and POPC \cite{altenbach84}).
    Simulations with Lipid14 parameters and \AA{}qvist ions are directly from Ref. \cite{catte16}, except that
    the concentration are determined with Eq. \ref{eq:conc}.
  }
  \todo{Simulation results with original Slipids and Dang ions to be added when we have the results.}
\end{figure*}

%After achieving accurate head group order parameter response with a cationic surfactant, 
%we advanced to quantifying the response to solutions with varying concentrations of salts, namely \ce{NaCl} and \ce{CaCl_2}.
The headgroup order parameter response to aqueous ionic concentration
can be used to measure ion binding affinity in experiments and simulations,
as discussed in section \ref{section:electrometer} and in previous literature~\cite{seelig87,catte16}.
The headgroup order parameter response of PC lipids to NaCl and CaCl$_2$ concentrations
from experiments (DPPC \cite{akutsu81} and POPC \cite{altenbach84}) and different simulation
models are shown in Fig. \ref{OrderParameterCHANGESnewMODELS}.
The simulation results of Lipid14 with \AA{}qvist ions~\cite{aqvist90} (from Ref. \citenum{catte16})
are shown together with the results from Lipid14 simulation
with ions by Dang~\cite{smith94,chang1999,dang2006} and from ECC-lipids simulations with ECC-ions.

As already discussed in a recent work by NMRlipids project~\cite{catte16},
the headgroup order parameters are almost unaffected by addition of NaCl
in Lipid14 simulations with \AA{}qvist ion model due to a very weak binding of Na$^+$
in PC bilayer. This is in agremeent with experimental data, in contrast
to almost all the other lipid models, which significantly overestimate
Na$^+$ binding in PC bilayers~\cite{catte16}. Despite the good performance
with NaCl, the response of headgroup order parameters to CaCl$_2$ concentration are
significantly overestimated in Lipid14 simulations with \AA{}qvist ion model,
see Fig.~\ref{OrderParameterCHANGESnewMODELS} and Ref.~\citenum{catte16}.

Wide range of data presented in previous work \cite{catte16} suggested
that CaCl$_2$ binding behaviour cannot be corrected by only improving
ion models. This was not, however, tested specifically for Lipid14 model, so we
ran also Lipid14 simulations with ions by Dang~\cite{smith94,chang1999,dang2006} 
and ECC-ions~\cite{jungwirth17-new-paper-to-be-published, kohagen16, Pluharova2014},
which have more realistic bulk behaviour than \AA{}qvist model~\cite{aqvist90}.
In line with previous work, the headgroup order parameters response
to CaCl$_2$ concentration was overestimated also with these ion models,
as seen in Figs. \ref{OrderParameterCHANGESnewMODELS} and \ref{??} (in SI), respectively
\todo{Add OP-response of Lipid14+Dang in Fig. \ref{OrderParameterCHANGESnewMODELS}
  and OP-response of Lipid14+ECC-ions plot in SI}.

Applying ECC correction also to lipids, introduced in section \ref{section:ecc},
brings the order parameter response to CaCl$_2$ concentration to a
good agreement with experiments, as shown in Fig. \ref{OrderParameterCHANGESnewMODELS}.
This is a significant improvement over previously introduced models,
which all overestimate the head group order parameter response to CaCl$_2$
concentration \cite{catte16}. The good agreement with experiments indicates
that the ECC corrected lipid model has a sufficient accuracy for realistic
studies of details of ions binding to lipid bilayers.

Ion density profiles along membrane normal 
from different simulations are shown in Fig.~\ref{fig:cacl-dens}.
\todo{This paragraph is to be finalized when we have the surface excess analysis
  done by using Eq.~\ref{surfexcess}.}
This is directly related to the amount of surface excess charge 
as shown along with ion density profiles in  Fig.~\ref{fig:cacl-dens}.
The density profiles from simulations with original Lipid14 \cite{dickson14}
and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
or the ion model by \AA{qvist}~\cite{aqvist90}
along with Lipid14 does not significantly change it 
(Headgroup order parameter responses for these models in SI).
The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
It is then likely that the models that overestimate head group order parameter response~\cite{catte16}
also overestimate the amount of bound cations.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities2.eps}
  \caption{\label{fig:cacl-dens}
    Number density of \ce{Ca^{2+}} and \ce{Cl^-} as a function of membrane normal axis
    for different force fields. Data for Lipid14 with \AA{}qvist ions are taken directly from Ref. \citenum{catte16}
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    Densities of~\ce{Cl^-}) and water are divided with 2 and 200, respectively, to visalize them
    with the same scale as \ce{Ca^{2+}}. The molar concentration in water is 350~mM in all systems
    presented here. 
    }
  \todo{PAVEL: draw phosphate position with its variance, add water density (scaled) and include the number of$\Gamma$-surface access.} \\
  \todo{JOE: Change the figure so that it contains a membrane background} \\
  \todo{Resuls with Lipid14+Dang to be added once done.}
\end{figure}

@@

This work can be reached as a repository containing all data at \url{zenodo.org:\dots\dots\dots} and as project \mbox{NMRlipids~VI} in \url{nmrlipids.blogspot.fi}.
